### 2024-05-04 thesis/chapters/03-design.tex
Fix accuracies in tables

The best feature subset from complete sets is picked after ranking the features according to their importance. An additional rule is that attributes cannot be added to the same set when they correlate very strongly  $|\mathrm{corr}| > 0.95$. The feature with a lower rank is added instead to the set.

The bivariate scores for ranking are the mean of point biserial \textbf{correlation} to every class label as a dichotomous variable, \textbf{Fisher score} (F statistic), and \textbf{Mutual information}. The correlation among features can reduce model's prediction power. The rank product combines the three latter scores into the ensemble. The comparison for the accuracy of the feature selection strategy is made in relation to the entire model accuracy distribution.

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim1-A.png}
        \caption{Time-domain features for 1 axis}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim1-A.png}
        \caption{Frequency-domain features for 3 axes}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim3-A.png}
        \caption{Time-domain features for 1 axis}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim3-A.png}
        \caption{Frequency-domain features for 3 axes}
    \end{subfigure}
    \caption{The value ranges of attributes for bearing A, depending on the number of directions that feature is aggregated out of}
    \label{fig:design:feature-range}
\end{figure}

Inside the interquartile range of three axis features the peak-to-peak is approximately between 2 - 22 $\mathrm{m/s}^2$, root-mean-square is 0.4 - 2.5 $\mathrm{m/s}^2$, average amplitude change represents 0.05 - 0.45 $\mathrm{m/s}^2$ of amplitude change in 20 $\mu\mathrm{s}$. In the frequency domain, the spectral centroid is 100 - 5900 Hz, roll-off frequencies arise below 5000 Hz, roll-on frequencies are below 400 Hz, and entropy occurs from 4 to 12 nats.

@@

\textbf{Standing fan} is model \emph{Kalorik~TKG~VT1037} (Fig.~\ref{fig:machine:fan}) and one unit is available to us. It serves as a test bed during the data logger development. The sensor is placed on the plastic casing at the back of the drive motor. The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}). It has a switch for 3 rotational speeds, which are approximately 19~Hz, 21~Hz, and 23~Hz ($\pm$ 0.18 Hz). Speed estimation was done by spectral analysis of audio (Fig.~\ref{fig:design:fan-speed}) in \emph{Spectroid} app and confirmed by 240 fps high-speed camera.

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/ksb-guard-rms.png}
        \caption{Vibration rms velocity dashboard}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/ksb-guard-spectrum.png}
        \caption{Vibration frequency analysis dashboard}
    \end{subfigure}
     \caption{KSB Guard cloud monitoring for pumps}
     \label{fig:design:ksb-guard}
\end{figure}

Logs from \textbf{KSB Guard} cloud monitoring tool contain vibration rms velocities and frequency spectra for two monitored KSB water pumps (Figure~\ref{fig:design:ksb-guard}). We were able to export the historical log of vibration velocity for last year at hourly intervals and sample frequency spectra.

>>>>

The best feature subset from complete sets is picked after ranking the features according to their importance. The bivariate scores for ranking are the mean of point biserial \textbf{correlation} to every class label as a dichotomous variable, \textbf{Fisher score} (F statistic), and \textbf{Mutual information}. The correlation among features can reduce model's prediction power. The rank product combines the three latter scores into the ensemble. The comparison for the accuracy of the feature selection strategy is made in relation to the entire model accuracy distribution.

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim1-A.png}
        \caption{Time-domain features for 1 axis}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim1-A.png}
        \caption{Frequency-domain features for 1 axes}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim3-A.png}
        \caption{Time-domain features for 3 axes}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim3-A.png}
        \caption{Frequency-domain features for 3 axes}
    \end{subfigure}
    \caption{The value ranges of attributes for bearing A, depending on the number of directions that feature is aggregated out of}
    \label{fig:design:feature-range}
\end{figure}

Inside the interquartile range of three axis features the peak-to-peak is between 4.89 - 11.39 $\mathrm{m/s}^2$, root-mean-square is 0.56 - 1.31 $\mathrm{m/s}^2$, average amplitude change represents 0.08 - 0.23 $\mathrm{m/s}^2$ of amplitude change in 20 $\mu\mathrm{s}$. In the frequency domain, the spectral centroid is in range of 1575 - 4175 Hz, roll-off frequencies arise above 246 and below 4476 Hz, roll-on frequencies are from 50 to 207 Hz, and entropy occurs from 7.57 to 10.94 nats.

@@

\textbf{Standing fan} is model \emph{Kalorik~TKG~VT1037} (Fig.~\ref{fig:machine:fan}) and one unit is available to us. It serves as a test bed during the data logger development. The sensor is placed on the plastic casing at the back of the drive motor. The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}). It has a switch for 3 rotational speeds, which are approximately 19~Hz, 21~Hz, and 22.7~Hz ($\Delta f$ = 0.18 Hz). Speed estimation was done by spectral analysis of audio (Fig.~\ref{fig:design:fan-speed}) in \emph{Spectroid} app and confirmed by 240 fps high-speed camera.

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/ksb-guard-rms.png}
        \caption{Vibration rms velocity dashboard}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/ksb-guard-spectrum.png}
        \caption{Vibration frequency analysis dashboard}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/sensor/ksb-cloud.jpg}
        \caption{KSB Guard Sensor Unit}
        \label{fig:design:ksb-device}
    \end{subfigure}
     \caption{KSB Guard cloud monitoring for pumps}
     \label{fig:design:ksb-guard}
\end{figure}

Logs from \textbf{KSB Guard} cloud monitoring tool contain vibration rms velocities and frequency spectra for two monitored KSB water pumps (Figure~\ref{fig:design:ksb-guard}). We were able to export the historical log of vibration velocity for last year at hourly intervals and sample frequency spectra. The sensor unit (Fig.~\ref{fig:design:ksb-device}) is permanently attached to KSB pumps on bearing in position no. 3.

### 2024-05-04 thesis/chapters/04-implementation.tex
Fix accuracies in tables

The tabular data is handled using \emph{Pandas}dataframes that are training batch models from \emph{scikit-learn} library and \emph{imbalanced-learn}, or online models from \emph{RiverML}. The wide variety of graphs and other visualizations are stylized with \emph{Matplotlib} and \emph{Seaborn}. Feature calculation is crafted according to mathematical formulas atop libraries \emph{Numpy}, \emph{SciPy}, and \emph{Time Series Feature Extraction Library}~(TSFEL).

>>>>

The tabular data is handled using \emph{Pandas} dataframes that are training batch models from \emph{scikit-learn} library and \emph{imbalanced-learn}, or online models from \emph{RiverML}. The wide variety of graphs and other visualizations are stylized with \emph{Matplotlib} and \emph{Seaborn}. Feature calculation is crafted according to mathematical formulas atop libraries \emph{Numpy}, \emph{SciPy}, and \emph{Time Series Feature Extraction Library}~(TSFEL).
